---
title       : How to tell if you're a Data Nerd
subtitle    : 
author      : redfalconx
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The idea is simple

1. Data Nerds can be identified based on the number of coursera data courses they've taken.
2. The app will calculate your likelihood of being a Data Nerd.
3. Values greater than 1 mean you're just a huge, gigantic Data Nerd. There is no helping you.

--- .class #id 

## The Formula


The formula is simple. It takes the number of courses and divides by 10.

---

## The function

The function looks like this:

```{r}
DataNerd <- function(courses) courses / 10

```

---

## Voila!

For example, if we put in 5 courses, it will return

You are this much of a Data Nerd

```{r echo=FALSE}

5/10
```

This will predict how much of a Data Nerd you are.

---
